---
title: COMP2550/COMP4450/COMP6445 - Data Science and Applied Machine Learning Assignment
---

```{r, warning=FALSE,message=FALSE,error=FALSE}
# load in packages
library(caret)
library(dplyr)
```


```{r}
# load the dataset
data_df <- read.csv("sample_users_100k.csv.bz2", sep="\t", stringsAsFactors = F)
```


Next, we coerce the `botscore` variable to be numeric and we correct abnormal values:
```{r warning=FALSE,error=FALSE}
# make botscore numerical and correct invalid data
data_df$botscore <- as.numeric(data_df$botscore)
toDel <- which(data_df$botscore < 0)
data_df <- data_df[-toDel,]
toDel <- which(is.na(data_df$botscore))
data_df <- data_df[-toDel,]
```
Finally, we construct the $\psi$ measure, defined as the ratio of friends (`friendsCount`) to followers (`followersCount`):
```{r}
# construct the $\psi$ measure from the previous tutorial
data_df$psi <- data_df$friendsCount / (data_df$followersCount + 0.01)
```


Visibly, out of the `r ncol(data_df)` features in `data_df`, many are of the type character (`chr`).
Some are already numerical (`num` and `int`) while other are logical and need to be transformed in a meaningful way.
We perform the following operations:

* we keep all numerical features and we drop entries with `NA` values;
* we convert `verified` to numerical (True to 1 and False to 0; `NA` to 0);
* for `location.objectType`, we convert "place" to 1, `NA` to 0;
* for `mcsize` (i.e. mean cascade size, the mean size of cascades started by a given user, [see full meaning in the paper here](https://arxiv.org/pdf/1802.09808.pdf): https://arxiv.org/pdf/1802.09808.pdf):  convert `NA` to 0.



Here we add our own features
```{r}
l <- as.numeric(as.Date(data_df$collectionDate) - as.Date(data_df$postedTime))
data_df$days_since_posted <- l

data_df$has_summary <- is.na(data_df$summary)
data_df$has_summary <- data_df$has_summary * 1

data_df$has_timezone <- is.na(data_df$twitterTimeZone)
data_df$has_timezone <- data_df$has_timezone * 1



data_df$words <- strsplit(sapply(gsub("[^[:alnum:][:space:]#]", "", data_df$summary), tolower), " ")

countHashOccurrences <- function(s) {
    s2 <- gsub("#","",s)
    return (nchar(s) - nchar(s2))
}
data_df$no_hashtags <- countHashOccurrences(data_df$summary)
data_df$no_hashtags[is.na(data_df$no_hashtags)] <- 0

data_df$median_wordlength <- as.numeric(lapply(lapply(data_df$words, nchar), median))
data_df$median_wordlength[is.na(data_df$median_wordlength)] <- 0

data_df$longest_word <- as.numeric(lapply(lapply(data_df$words, nchar), (function (x) max(x, 0))))
data_df$longest_word[is.na(data_df$longest_word)] <- 0
```


```{r}
# Deal with missing value and category variables: 
features = c(
  'listedCount', # drop na
  'favoritesCount', # drop na
  'friendsCount', # drop na
  'followersCount', # drop na
  'verified', # convert True to 1 and False to 0; na to 0 
  'location.objectType', # convert "place" to 1, na to 0 
  'mcsize', # convert na to 0
  'influence', # drop na
  'influence_percentile', # drop na
  'tweetsCount', # drop na
  'retweetsCount', # drop na
  'days_since_posted',
  'has_summary',
  'has_timezone',
  'no_hashtags', # maybe
  'median_wordlength', # maybe
  'longest_word', # maybe
  'psi', 
  'botscore' # drop na
)

# keep only selected features
data_df <- data_df[, features]

# clean verified
data_df$verified[is.na(data_df$verified)] <- F
data_df$verified <- data_df$verified * 1

# clean location.objectType
data_df$location.objectType[data_df$location.objectType == "place"] <- 1
data_df$location.objectType[is.na(data_df$location.objectType)] <- 0
data_df$location.objectType <- as.numeric(data_df$location.objectType)

# clean mcsize
data_df$mcsize[is.na(data_df$mcsize)] <- 0

# remove non-complete entries
toKeep <- rowSums(is.na(data_df)) == 0
data_df <- data_df[toKeep, ]
```


```{r}
# first construct a train and a test sample, each of 1000 users
#set.seed(287)
#ample2k <- sample_n(tbl = data_df, size = 2000, replace = F)
##sample2k <- sample_n(tbl = data_df, size = 82454, replace = F)

#data_train <- sample2k[1:1000,]
#data_test <- sample2k[1001:2000,]
##data_train <- sample2k[1:60000,]
##data_test <- sample2k[60000:82454,]

data_train <- sample_n(tbl = data_df, size = 82454, replace = F)
#data_train <- sample_n(tbl = data_df, size = 4000, replace = F)
```


```{r}
metrics <- data.frame(matrix(data = NA, nrow = 3, ncol = 0))
```


```{r}
#fitControl <- trainControl(
#  # Repeated 10–fold CV 
#  method = "repeatedcv",
#  number = 10,
#  # repeated 10 times
#  repeats = 10,
#  returnResamp = "all")

#model_rf <- train(botscore ~ ., data = data_train, 
#                  method = "ranger", trControl = fitControl)

#mean(model_rf$resample$RMSE)
```

```{r}
data_train_preproc <- preProcess(select(data_train, - botscore), 
                                 method = c("center", "scale", "YeoJohnson"))#, "nzv", "pca"))
                                # method = c("center", "scale", "YeoJohnson", "nzv", "pca"))

train_df <- predict(data_train_preproc, data_train)
#test_df <- predict(data_train_preproc, data_test)

data_train_preproc
```


```{r}
fitControl <- trainControl(
  method = "repeatedcv",
  number = 10,
  repeats = 5,
  returnResamp = "all")

model_rfpp <- train(botscore ~ ., data = train_df, 
                  method = "ranger", trControl = fitControl)
###predict the outcome on a test set
model_rfpp_pred <- predict(model_rfpp, train_df)

#metrics <- cbind(metrics, RFpp = postResample(pred = model_rfpp_pred, 
#                                                obs = test_df$botscore) )
mean(model_rfpp$resample$RMSE)
```


```{r}
#fitControl <- trainControl(
#  method = "oob",
#  number = 5,
#  returnResamp = "all")

#model_rf_2 <- train(botscore ~ ., data = train_df, 
#                  method = "ranger", trControl = fitControl)

#mean(model_rf_2$resample$RMSE)
```

```{r}
#fitControl <- trainControl(
#  method = "repeatedcv",
#  number = 7,
#  repeats = 3,
#  returnResamp = "all")

#model_rf_1 <- train(botscore ~ ., data = data_train, 
#                  method = "ranger", trControl = fitControl)
# predict the outcome on a test set
#model_rfpp_pred <- predict(model_rfpp, train_df)

#metrics <- cbind(metrics, RFpp = postResample(pred = model_rfpp_pred, 
#                                                obs = test_df$botscore) )
#mean(model_rf_1$resample$RMSE)
```

#####################################################################


```{r}
# load the dataset
testing_set <- read.csv("testing_set_features.csv.bz2", sep="\t", stringsAsFactors = F)
```

```{r}
# construct the $\psi$ measure from the previous tutorial
testing_set$psi <- testing_set$friendsCount / (testing_set$followersCount + 0.01)
```

Here we add our own features
```{r}
l <- as.numeric(as.Date(testing_set$collectionDate) - as.Date(testing_set$postedTime))
testing_set$days_since_posted <- l

testing_set$has_summary <- is.na(testing_set$summary)
testing_set$has_summary <- testing_set$has_summary * 1

testing_set$has_timezone <- is.na(testing_set$twitterTimeZone)
testing_set$has_timezone <- testing_set$has_timezone * 1



testing_set$words <- strsplit(sapply(gsub("[^[:alnum:][:space:]#]", "", testing_set$summary), tolower), " ")

countHashOccurrences <- function(s) {
    s2 <- gsub("#","",s)
    return (nchar(s) - nchar(s2))
}
testing_set$no_hashtags <- countHashOccurrences(testing_set$summary)

testing_set$median_wordlength <- as.numeric(lapply(lapply(testing_set$words, nchar), median))
testing_set$median_wordlength[is.na(testing_set$median_wordlength)] <- 0

testing_set$longest_word <- as.numeric(lapply(lapply(testing_set$words, nchar), (function (x) max(x, 0))))
testing_set$longest_word[!is.finite(testing_set$median_wordlength)] <- 0
```


```{r}
# Deal with missing value and category variables: 
features = c(
  'user_id', # WE NEED THIS
  'listedCount', # drop na
  'favoritesCount', # drop na
  'friendsCount', # drop na
  'followersCount', # drop na
  'verified', # convert True to 1 and False to 0; na to 0 
  'location.objectType', # convert "place" to 1, na to 0 
  'mcsize', # convert na to 0
  'influence', # drop na
  'influence_percentile', # drop na
  'tweetsCount', # drop na
  'retweetsCount', # drop na
  'days_since_posted',
  'has_summary',
  'has_timezone',
  'no_hashtags', # maybe
  'median_wordlength', # maybe
  'longest_word', # maybe
  'psi'
)

# keep only selected features
testing_set <- testing_set[, features]

# clean verified
testing_set$verified[is.na(testing_set$verified)] <- F
testing_set$verified <- testing_set$verified * 1

# clean location.objectType
testing_set$location.objectType[testing_set$location.objectType == "place"] <- 1
testing_set$location.objectType[is.na(testing_set$location.objectType)] <- 0
testing_set$location.objectType <- as.numeric(testing_set$location.objectType)

# clean mcsize
testing_set$mcsize[is.na(testing_set$mcsize)] <- 0




# remove non-complete entries
toKeep <- rowSums(is.na(testing_set)) == 0

# keep track of removed rows and assign predictions to them
deleted <- data.frame(testing_set[!toKeep,])
###deleted <- rename(deleted, user_id = 1)
deleted$botscore <- NA
deleted$psi_percentile <- NA


testing_set <- testing_set[toKeep, ]

```

```{r}
myecdf <- ecdf(testing_set$psi)
testing_set$psi_percentile <- myecdf(testing_set$psi)
```

```{r}
test_df <- predict(data_train_preproc, testing_set[,c(  'listedCount', # drop na
                                                        'favoritesCount', # drop na
                                                        'friendsCount', # drop na
                                                        'followersCount', # drop na
                                                        'verified', # convert True to 1 and False to 0; na to 0 
                                                        'location.objectType', # convert "place" to 1, na to 0 
                                                        'mcsize', # convert na to 0
                                                        'influence', # drop na
                                                        'influence_percentile', # drop na
                                                        'tweetsCount', # drop na
                                                        'retweetsCount', # drop na
                                                        'days_since_posted',
                                                        'has_summary',
                                                        'has_timezone',
                                                        'no_hashtags', # maybe
                                                        'median_wordlength', # maybe
                                                        'longest_word', # maybe
                                                        'psi')])
```


```{r}
###testing_set$botscore <- predict(model_rf, testing_set)#, type="raw")
testing_set$botscore <- predict(model_rfpp, test_df)

result <- data.frame(testing_set)
#result <- subset(result, select=c(user_id,is_bot))
result <- rbind(result, deleted)

result <- result[, c("user_id", "botscore")]
#table(result$botness)
```

```{r}
write.csv(result, file = "regressor_predictions_2.csv")
```

```{r}

```

